Full-day, in home validation of infant body position measurements from inertial sensors

### 2023-02-18 manuscript.Rmd
metrics plot

```{r setup, include = FALSE}
library(papaja)
library(knitr)
library(patchwork)
library(scales)
library(tidyverse)
library(rstatix)
```

@@

## Goal 1: Optimize and validate body position classification model
<!-- group_split_metrics, generated from group_split_comparison in this proj, stable copy in data/ -->
```{r}
metrics <- read_csv("data/group_split_metrics.csv")

>>>>

```{r setup, include = FALSE}
library(papaja)
library(knitr)
library(patchwork)
library(scales)
library(ggforce)
library(tidyverse)
library(rstatix)
```

@@

## Goal 1: Optimize and validate body position classification model
<!-- group_split_metrics, generated from group_split_comparison in this proj, stable copy in data/ -->
```{r metrics, warning=FALSE, fig.cap="Metrics", fig.align="center", fig.width=5, fig.height=8}
metrics <- read_csv("data/group_split_metrics.csv") %>% 
  filter(model %in% c("group", "split")) %>% 
  mutate(Model = factor(model, levels = c("group", "split"), labels = c("Group", "Individual")))

metrics_long <- metrics %>% pivot_longer(cols = `Overall Accuracy`:Kappa, 
                                         names_to = "metric",
                                         values_to = "value")

metric_plot <- function(ds, met) {
  ds %>% filter(metric == met) %>% 
    ggplot(aes(x = Model, y = value, shape = Model)) + 
    geom_sina(alpha = .7, fill = "orange", size = 4, maxwidth = .5) +
    stat_summary(fun = "mean", mapping = aes(x = Model, y = value), shape = "-", fill = "black", size = 4) + 
    scale_shape_manual(guide = "none", values = c(21,23)) + 
    ylim(0, 1) + ylab(met) + xlab("") + 
    theme(plot.title.position = "plot",
          axis.title.y = element_text(size = 13),
          axis.text.y = element_text(size = 11),
          axis.text.x = element_text(size = 13))
}
metric_labels <- c("Overall Accuracy", "Balanced Accuracy", "F1", "Sensitivity", "Pos Pred Value", "Kappa")
title_labels <- c("A. Overall Accuracy", "B. Balanced Accuracy", "C. F1 Score", "D. Sensitivity", "E. Pos. Pred. Value", "F. Kappa")
metric_plots <- map(metric_labels, ~ metric_plot(metrics_long, .x)) %>% map2(., title_labels, ~.x + ggtitle(.y))
(metric_plots[[1]] + metric_plots[[2]])/(metric_plots[[3]]+metric_plots[[4]])/(metric_plots[[5]] + metric_plots[[6]])
